Why is Stochastic Lambda > Deterministic?

### 2022-04-26 notes/understanding stochastic lambda.Rmd

vit_list_yr <- 
  single_years %>% 
  map(~{
    vit_list_det_ff = c(
      list(
        vit_surv = surv_det(.x, habitat = "1-ha"),
        vit_size = size_det(.x, habitat = "1-ha"),
        vit_flwr = flwr_det(.x, habitat = "1-ha"),
        vit_size_sdlg = size_sdlg_det(.x, habitat = "1-ha"),
        vit_surv_sdlg = surv_sdlg_det(.x, habitat = "1-ha")
      ),
      vit_other_ff)
    })

@@

```{r warning=FALSE, class.source = 'fold-hide'}
vit_list_det_ff = c(
  list(
    vit_surv = surv_det(two_yrs, habitat = "1-ha"),
    vit_size = size_det(two_yrs, habitat = "1-ha"),
    vit_flwr = flwr_det(two_yrs, habitat = "1-ha"),
    vit_size_sdlg = size_sdlg_det(two_yrs, habitat = "1-ha"),
    vit_surv_sdlg = surv_sdlg_det(two_yrs, habitat = "1-ha")
  ),
  vit_other_ff)

@@

```{r warning=FALSE, class.source = 'fold-hide'}
## forets fragments
vit_list_stoch_ff = c(
  list(
    vit_surv = surv_raneff(two_yrs, habitat = "1-ha"),
    vit_size = size_raneff(two_yrs, habitat = "1-ha"),
    vit_flwr = flwr_raneff(two_yrs, habitat = "1-ha"),
    vit_size_sdlg = size_sdlg_raneff(two_yrs, habitat = "1-ha"),
    vit_surv_sdlg = surv_sdlg_raneff(two_yrs, habitat = "1-ha")
  ), 
  vit_other_ff)

>>>>

vit_list_yr <- 
  single_years %>% 
  filter(habitat == "1-ha") %>% 
  map(~{
    vit_list_det_ff = c(
      list(
        vit_surv = surv_det(.x),
        vit_size = size_det(.x),
        vit_flwr = flwr_det(.x),
        vit_size_sdlg = size_sdlg_det(.x),
        vit_surv_sdlg = surv_sdlg_det(.x)
      ),
      vit_other_ff)
    })

@@

```{r warning=FALSE, class.source = 'fold-hide'}
vit_list_det_ff = c(
  list(
    vit_surv = surv_det(two_yrs),
    vit_size = size_det(two_yrs),
    vit_flwr = flwr_det(two_yrs),
    vit_size_sdlg = size_sdlg_det(two_yrs),
    vit_surv_sdlg = surv_sdlg_det(two_yrs)
  ),
  vit_other_ff)

@@

```{r warning=FALSE, class.source = 'fold-hide'}
## forets fragments
vit_list_stoch_ff = c(
  list(
    vit_surv = surv_raneff(two_yrs),
    vit_size = size_raneff(two_yrs),
    vit_flwr = flwr_raneff(two_yrs),
    vit_size_sdlg = size_sdlg_raneff(two_yrs),
    vit_surv_sdlg = surv_sdlg_raneff(two_yrs)
  ), 
  vit_other_ff)
